### 2024-09-11 getting-started.qmd
20240911 - loading and saving data

@@

>>>>

Here is how you load a `.RData` file using a *relative path* (i.e., a path relative to the working directory, where the working directory is represented by a period):

@@

The following code loads a file from an *absolute path*:

nfl_players <- read.csv("C:/Users/myusername/nfl_players.RData")
```

Here is how you load a `.csv` file:

nfl_players <- read.csv("./data/nfl_players.csv") # relative path
nfl_players <- read.csv("C:/Users/myusername/nfl_players.csv") # absolute path
```

## Save a Data Frame {#sec-gettingStartedSaveData}

Here is how you save a `.RData` file using a *relative path*:

save(
  nfl_players,
  file = "./data/nfl_players.RData")
```

The following code saves a file to an *absolute path*:

save(
  nfl_players,
  file = "C:/Users/myusername/nfl_players.RData")
```

Here is how you save a `.csv` file:

write.csv(
  nfl_players,
  file = "./data/nfl_players.csv") # relative path

write.csv(
  nfl_players,
  file = "C:/Users/myusername/nfl_players.csv") # absolute path
```
